Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-10-31 manuscript_responses_v1.tex
update Xdumusque

\item[]  RESPONSE:  The purpose of the study using the SOAP simulations was to consider a simplified setting in which we can isolate the effects of a spot and a facula on the various activity measures.  There are many different possible combinations of spots and faculae that could be considered, but we preferred to keep the activity level simple in order to aid in the interpretation of the results.  The real observations used help to provide insight into how the various activity measures behave with realistic activity levels.  The temperature of the spot and facula has now been added to the beginning of Section 4.  The temperature of the spot is XXXX and the temperature of the facula is XXXX.  {\color{magenta} Xavier, please address the Editor question about the temperature of the spot/facula - I added a place for it at the beginning of Section 4}

>>>>

\item[]  RESPONSE:  The purpose of the study using the SOAP simulations was to consider a simplified setting in which we can isolate the effects of a spot and a facula on the various activity measures.  There are many different possible combinations of spots and faculae that could be considered, but we preferred to keep the activity level simple in order to aid in the interpretation of the results.  The real observations used help to provide insight into how the various activity measures behave with realistic activity levels.  The temperature of the spot and facula has now been added to the beginning of Section 4. The temperature difference of the spot with the photosphere is $\Delta T_{spot} = -663$ K and the temperature difference of the facula is dependant on the centre-to-limb angle $\theta$,  $\Delta T_{plage} = 250.9 - 407.7\,\cos{\theta} + 190.9\,\cos^2 \theta$ K (Meunier et al. 2010). 

### 2018-10-31 manuscript_v2.tex
update Xdumusque

For the simulations discussed below, a star similar to the Sun was modelled with a solar disc of one solar radius seen equator-on, and a stellar rotational period set to 25.0 days.
The stellar effective temperature is set to 5778 K, and a quadratic limb-darkening relation with linear and quadratic coefficients 0.29 and 0.34, respectively \citep[][]{Oshagh-2013a, Claret-2011}.
{\color{magenta} The temperature of the facula is XXXX and the temperature of the spot is XXXX.}
In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generated with a width of 40 \kms\, and considering initial spectra with a spectral resolution of R=115'000.

>>>>

For the simulations discussed below, a star similar to the Sun was modelled with a solar disc of one solar radius seen equator-on, and a stellar rotational period set to 25.0 days.
The stellar effective temperature is set to 5778 K, and a quadratic limb-darkening relation with linear and quadratic coefficients 0.29 and 0.34, respectively \citep[][]{Oshagh-2013a, Claret-2011}. {\bf The temperature difference of the spot with the photosphere is $\Delta T_{spot} = -663$ K and the temperature difference of the facula is dependant on the centre-to-limb angle $\theta$,  $\Delta T_{plage} = 250.9 - 407.7\,\cos{\theta} + 190.9\,\cos^2 \theta$ K \citep[][]{Meunier-2010a}}.
In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generated with a width of 40 \kms\, and considering initial spectra with resolution of R=115'000.
